taxize - taxonomic search and retrieval in R

### 2013-06-04 inst/doc/taxize_withcode_appB.Rnw
chunk names

<<lower>>=
# look for cases where taxonomic resolution in abundance data is higher than in trait data:
# here we take the trait-values for the lower resolution
for(i in which(is.na(lookup$traits))){
  if(is.data.frame(lookup_classi[[i]])){
    matches <- tolower(lookup_classi[[i]]$ScientificName) %in% traits$taxon_cleaned
    if(any(matches)){
      lookup$traits[i] <- tolower(lookup_classi[[i]]$ScientificName[matches])
      lookup$type[i] <- lookup_classi[[i]]$Rank[matches]
    }
  }
}
lookup
@

@@

<<>>=
# look for cases taxonomic resolution in abundance data is lower than in trait data,
# here we need to aggregate the trait-values (eg. median value for modality)

@@

Finally we have one taxon left. We remove this from our dataset:
<<>>=
abundances <- abundances[!abundances$taxon == lookup$taxon[is.na(lookup$traits)], ]
@

@@

<<>>=
# species (as matched with trait table) by site matrix
abundances$traits_taxa <- lookup$traits[match(tolower(abundances$taxon), lookup$taxon)]

>>>>

<<higher_resolution>>=
# look for cases where taxonomic resolution in abundance data is higher than in trait data:
# here we take the trait-values for the lower resolution
for(i in which(is.na(lookup$traits))){
  if(is.data.frame(lookup_classi[[i]])){
    matches <- tolower(lookup_classi[[i]]$ScientificName) %in% traits$taxon_cleaned
    if(any(matches)){
      lookup$traits[i] <- tolower(lookup_classi[[i]]$ScientificName[matches])
      lookup$type[i] <- lookup_classi[[i]]$Rank[matches]
    }
  }
}
lookup
@

@@

<<lower_resolution>>=
# look for cases taxonomic resolution in abundance data is lower than in trait data,
# here we need to aggregate the trait-values (eg. median value for modality)

@@

Finally we have one taxon left. We remove this from our dataset:
<<na_omit>>=
abundances <- abundances[!abundances$taxon == lookup$taxon[is.na(lookup$traits)], ]
@

@@

<<matrices>>=
# species (as matched with trait table) by site matrix
abundances$traits_taxa <- lookup$traits[match(tolower(abundances$taxon), lookup$taxon)]
